### 2019-05-14 report/chapter04.Rnw
presentation

\subsubsection{Thompson and Sharp's Test: Weighted Linear Regression Random Effects Test}
A method proposed in \citet{thompson.sharp} allows for between study heterogeneity. Let $\tau^2$ be equal to \ref{Tau.definition}. The effect size estimates are then assumed to be distributed as in \ref{t.sharp.regression}.

\begin{align}
y_{i} \sim N(\beta_{0} + \beta{1}x_{i}, v_{i} + \tau^2) \label{t.sharp.regression}
\end{align}

Then, a weighted regression is carried out with weights $1/v_{i}^\star$ based on the inverse of the variance as in \ref{ranef.study.variance}. Analogous to Edger's test, $\beta_{0}$ is then tested with respect to the null hypothesis $\beta{0} = 0$.

@@

\begin{align}
y_{i} = \arcsin{e_{t}/n_{t}} - \arcsin{e_{c}/n_{c}}// 
v_{i} = 1/4n_{t} + +/4n_{c}
\end{align}

@@

\subsection{Adjustment by Regression}
There are multiple ways to adjust for small study effects by regression. The general idea is to regress the effect size of a study with a variance of zero based on the given effects and variances.

@@

\begin{align}
y_{i}& = \beta_{0} + \beta{1}(\sqrt{v_{i} + \tau^2}) + \epsilon_{i}(\sqrt{s_{i} + \tau^2}), \stackrel{\textrm{iid}}{\sim} N(0,1)  \ref{limitmeta.regression}
\end{align}

$\beta{1}$ represents the bias introduced by small study effects, as can be seen when looking at \ref{limitmeta.infinitesample}

\begin{align}
\mathbb{E}((y_{i} - \beta_{})/\sqrt{v_{i}}) \rightarrow \beta_{1} \textrm{if} \sqrt{v_{i}} \rightarrow \infty \\
\mathbb{E}(y_{i}) \rightarrow \beta_{0} + \beta_{1}\tau \textrm{if} \sqrt{v_{i}} \rightarrow 0 
\end{align}

After estimating $\tau^2$, one can estimate $\beta_{0}$ and $\beta_{1}$ as seen before e.g. in Thompson and Sharp's Test with weights also equal to Thompson and Sharp's Test.

>>>>

\subsubsection{Thompson and Sharp's Test: Weighted Linear Regression Random Effects Test} \label{Thompson}
A method proposed in \citet{thompson.sharp} allows for between study heterogeneity. Let $\tau^2$ be equal to \ref{Tau.definition}. The effect size estimates are then assumed to be distributed as in \ref{t.sharp.regression}.

\begin{align}
y_{i} \sim N(\beta_{0} + \beta_{1}x_{i}, v_{i} + \tau^2) \label{t.sharp.regression}
\end{align}

Then, a weighted regression is carried out with weights $1/v_{i}^\star$ based on the inverse of the variance as in \ref{ranef.study.variance}. Analogous to Egger's test, $\beta_{0}$ is then tested with respect to the null hypothesis $\beta_{0} = 0$.

@@

\begin{align}
y_{i} = \arcsin{e_{t}/n_{t}} - \arcsin{e_{c}/n_{c}} \\
v_{i} = 1/4n_{t} + +/4n_{c}
\end{align}

@@

\subsection{Adjustment by Regression}
There are multiple ways to adjust for small study effects by regression. The general idea is to extrapolate the effect size of a study with a variance of zero based on the given effects and variances.

@@

\begin{align}
y_{i}& = \beta_{0} + \beta_{1}(\sqrt{v_{i} + \tau^2}) + \epsilon_{i}(\sqrt{s_{i} + \tau^2}), \epsilon_{i} \stackrel{\textrm{iid}}{\sim} N(0,1)  \label{limitmeta.regression}
\end{align}

$\beta_{1}$ represents the bias introduced by small study effects, as can be seen when looking at \ref{limitmeta.infinitesample}

\begin{align}
\mathbb{E}((y_{i} - \beta_{0})/\sqrt{v_{i}}) \rightarrow \beta_{1} \textrm{ if } \sqrt{v_{i}} \rightarrow \infty \label{limitmeta.infinitesample} \\
\mathbb{E}(y_{i}) \rightarrow \beta_{0} + \beta_{1}\tau \textrm{if} \sqrt{v_{i}} \rightarrow 0 
\end{align}

After estimating $\tau^2$, one can estimate $\beta_{0}$ and $\beta_{1}$ as seen before e.g. in Thompson and Sharp's Test with weights also equal to Thompson and Sharp's Test (see \ref{Thompson}).
